Lazy Linearity for a Core Functional Language

### 2025-11-25 popl26.tex
More acknowledgments

  This
  work was supported by national funds through Fundação para a Ciência e a Tecnologia, I.P. (FCT) under projects UID/50021/2025 and UID/PRR/50021/2025.

>>>>

We would like to thank Arnaud Spiwack for many insightful discussions on
linearity in Core and the reviewers for their feedback, which improved the
paper significantly. This work was supported by Well-Typed LLP and by
national funds through Fundação para a Ciência e a Tecnologia, I.P. (FCT)
under projects UID/50021/2025 and UID/PRR/50021/2025.
